---
title: "Indomie"
author: "Edwina"
date: "1/23/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
library(devtools)
install_github("nurandi/katadasaR")
install_github("lmullen/gender")
```


```{r }
library(textclean)
library(katadasaR)
library(tokenizers)
library(wordcloud)
library(dplyr)
library(tidyverse)
```

Tarik Data 
```{r pressure, echo=FALSE}
library(readr)
lgbtData <- read_csv("lgbt_3.csv")
head(lgbtData)
```

```{r pressure, echo=FALSE}

lgbtData <- lgbtData$Comment %>% as.character()

head(lgbtData)
lgbtSomeData<-as_data_frame(table(lgbtData))
lgbtSomeData
#some_tweets<-lgbt_1
#some_txt <- data.frame(as.list(some_tweets))  
#some_tweets <- searchTwitter('Indomie', n=1000, lang='en')
#some_txt <- sapply(some_tweets, function(x) x$getText()) 
#write.csv(some_txt, file = 'dataIndomie.csv')
```


```{r}
#pre processing with GSUB
lgbtDataG <- gsub("\n", "", lgbtData$Comment)
lgbtDataG <- gsub(" (RT|via)((?:\\b\\W*@\\w+)+)", "", lgbtDataG) 
lgbtDataG <- gsub("@\\w+", "", lgbtDataG)
lgbtDataG <- gsub("[[:punct:]]", "", lgbtDataG)
lgbtDataG <- gsub("[[:digit:]]", "", lgbtDataG)
lgbtDataG <- gsub("http\\w+", "", lgbtDataG)
lgbtDataG <-gsub("[ \t]{2,}", "", lgbtDataG)
lgbtDataG <- gsub("^\\s+|\\s+$", "", lgbtDataG)
lgbtDataG <- gsub("note", "", lgbtDataG)
lgbtDataG <- gsub("https\\w+", "was", lgbtDataG)
head(lgbtDataG)

```
```{r}
lgbtDataC <-lgbtData$Comment
str(lgbtDataC)
```
```{r}
library(qdap)
tolower(lgbtDataC)
removePunctuation(lgbtDataC)
removeNumbers(lgbtDataC)
stripWhitespace(lgbtDataC)

bracketX(lgbtDataC)

```

Membuat build 
```{r}
library(tm)

lgbtDataC_src <- VectorSource(lgbtDataC)
```

Now that we’ve converted our vector to a Source object, we pass it to another tm function, VCorpus(), to create our volatile corpus. The VCorpus object is a nested list, or list of lists. At each index of the VCorpus object, there is a PlainTextDocument object, which is essentially a list that contains the actual text data (content), as well as some corresponding metadata (meta) which can help to visualize a VCorpus object and to conceptualize the whole thing.
```{r}
# Make a volatile corpus: tweets_corpus
lgbtDataC_corpus <- VCorpus(lgbtDataC_src)
# Print out the tweets_corpus
lgbtDataC_corpus

#Coba index 15
lgbtDataC_corpus[[15]][1]

#Structure
str(lgbtDataC_corpus[[15]])
```

Cleanning & Preprocessing Data
```{r}
head(lgbtDataC_corpus)

```




Cleaning Data, Ubah ke data lowercase
```{r}
#cleaning data
some_txt = sapply(some_tweets, function(x) x$getText())
# remove retweet entities
some_txt = gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", some_txt)
# remove at people
some_txt = gsub("@\\w+", "", some_txt)
# remove punctuation
some_txt = gsub("[[:punct:]]", "", some_txt)
# remove numbers
some_txt = gsub("[[:digit:]]", "", some_txt)
# remove html links
some_txt = gsub("http\\w+", "", some_txt)
# remove unnecessary spaces
some_txt = gsub("[ \t]{2,}", "", some_txt)
some_txt = gsub("^\\s+|\\s+$", "", some_txt)
some_txt = gsub("note", "", some_txt)
some_txt = gsub("and", "", some_txt)
some_txt = gsub("for", "", some_txt)
some_txt = gsub("this", "", some_txt)
some_txt = gsub("with", "", some_txt)
some_txt = gsub("was", "", some_txt)
some_txt = gsub("https\\w+", "was", some_txt)
# define "tolower error handling" function 
try.error = function(x)
{
  # create missing value
  y = NA
  # tryCatch error
  try_error = tryCatch(tolower(x), error=function(e) e)
  # if not an error
  if (!inherits(try_error, "error"))
    y = tolower(x)
  # result
  return(y)
}
```

```{r}
# lower case using try.error with sapply 
some_txt = sapply(some_txt, try.error)
# remove NAs in some_txt
some_txt = some_txt[!is.na(some_txt)]
names(some_txt) = NULL
write.csv(some_txt, file = 'dataIndomieCleaned.csv')
```


Sentiment Analysis dengan NRC
```{r}
twiter <-read.csv("dataIndomieCleaned.csv",stringsAsFactors = FALSE)
review <- as.character(twiter$x)
#Calls the NRC sentiment dictionary to calculate the presence of eight different emotions and their corresponding valence in a text file.
get_nrc_sentiment('happy')
get_nrc_sentiment('excitement')
s<-get_nrc_sentiment(review)
review_combine<-cbind(twiter$x,s)
par(mar=rep(3,4))
barplot(colSums(s),col=rainbow(10),ylab='count',main='sentiment analisis')
```


Klasifikasi dg Naive Bayes dan Word Cloud
```{r}
# classify emotion
class_emo = classify_emotion(twiter, algorithm="bayes", prior=1.0)
# get emotion best fit
emotion = class_emo[,7]
# substitute NA's by "unknown"
emotion[is.na(emotion)] = "unknown"
# classify polarity
class_pol = classify_polarity(twiter, algorithm="bayes")
# get polarity best fit
polarity = class_pol[,4]

sent_df = data.frame(text=twiter, emotion=emotion,
                     polarity=polarity, stringsAsFactors=FALSE)
sent_df = within(sent_df,
                 emotion <- factor(emotion, levels=names(sort(table(emotion), decreasing=TRUE))))
write.csv(sent_df, file = 'dataSentimenIndomie.csv')
```


```{r}
head(sent_df,20)
table(sent_df$emotion)
docs <- Corpus(VectorSource(twiter))
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
KataKata <- data.frame(word = names (v), freq=v)
head(KataKata,10)
set.seed(1234)
wordcloud(words = KataKata$word, freq = KataKata$freq, scale=c(5.2,.6), min.freq=20, max.words=200, random.order=FALSE, random.color=TRUE, rot.per=0.4, colors=brewer.pal(8, "Dark2"))


```
Plot Sentimen Emosional 

```{r}
plotSentiments1 <- function(sentiment_dataframe, title) 
    {
      library(ggplot2)
      ggplot(sentiment_dataframe, aes(x=emotion)) + 
        geom_bar(aes(y=..count.., fill=emotion)) + 
        scale_fill_brewer(palette="Dark2") + 
        ggtitle(title) + 
        theme(legend.position="right") + 
        ylab("Number of Tweets") + 
        xlab("Emotion Categories")
    }
#plotting tweets emotions
plotSentiments1(sent_df, "Analisis Sentimen Pencarian : Indomie (EN)")
View(polarity)

```

Plot Sentimen Polarisasi
```{r}
plotSentiments2 <- function(sent_df, title)
    {
      library(ggplot2)
      ggplot(sent_df, aes(x=polarity)) +
        geom_bar(aes(y=..count.., fill=polarity)) +
        scale_fill_brewer(palette="RdGy") +
        ggtitle(title) +
        theme(legend.position="right") +
        ylab("Number of Tweets") +
        xlab("Polarity Categories")
}
#plotting tweets polarity
plotSentiments2(sent_df, "Analisis Sentimen Pencarian : Indomie (EN)")
```


```{r}
ui <- fluidPage(
    titlePanel("Sentiment Analysis INDOMIE [EN]"),
        mainPanel(
            
            tabsetPanel(type = "tabs",
                        tabPanel("Wordcloud", plotOutput("Wordcloud")),
                        tabPanel("NRC", plotOutput("NRC")), 
                        tabPanel("Naive Bayes - Emotion", plotOutput('NBEmotion')),
                        # Output Data Dalam Tabel
                        tabPanel("Naive Bayes - Polarity", plotOutput("NBPolarity"))
                        
                        )
        )
    )
# SERVER
server <- function(input, output) {
  
  
  
    # Output Data
    output$NRC <-renderPlot({
        twiter <-read.csv("dataIndomieCleaned.csv",stringsAsFactors = FALSE)
        review <- as.character(twiter$x)
        #Calls the NRC sentiment dictionary to calculate the presence of eight different emotions and their corresponding valence in a text file.
        get_nrc_sentiment('happy')
        get_nrc_sentiment('excitement')
        s<-get_nrc_sentiment(review)
        review_combine<-cbind(twiter$x,s)
        par(mar=rep(3,4))
        barplot(colSums(s),col=rainbow(10),ylab='count',main='sentiment analisis')
    })

    output$Wordcloud <- renderPlot({
      
      # classify emotion
      class_emo = classify_emotion(twiter, algorithm="bayes", prior=1.0)
      # get emotion best fit
      emotion = class_emo[,7]
      # substitute NA's by "unknown"
      emotion[is.na(emotion)] = "unknown"
      # classify polarity
      class_pol = classify_polarity(twiter, algorithm="bayes")
      # get polarity best fit
      polarity = class_pol[,4]
      
      sent_df = data.frame(text=twiter, emotion=emotion,
                           polarity=polarity, stringsAsFactors=FALSE)
      sent_df = within(sent_df,
                       emotion <- factor(emotion, levels=names(sort(table(emotion), decreasing=TRUE))))
      write.csv(sent_df, file = 'dataSentimenIndomie.csv')
      head(sent_df,20)
      table(sent_df$emotion)
      docs <- Corpus(VectorSource(twiter))
      dtm <- TermDocumentMatrix(docs)
      m <- as.matrix(dtm)
      v <- sort(rowSums(m),decreasing=TRUE)
      KataKata <- data.frame(word = names (v), freq=v)
      head(KataKata,10)
      set.seed(1234)
      wordcloud(words = KataKata$word, freq = KataKata$freq, scale=c(5.2,.6), min.freq=20, max.words=200, random.order=FALSE, random.color=TRUE, rot.per=0.4, colors=brewer.pal(8, "Dark2"))
     }, height=600)
    
    
    output$NBEmotion <- renderPlot({
      plotSentiments1 <- function(sentiment_dataframe, title) 
        {
          library(ggplot2)
          ggplot(sentiment_dataframe, aes(x=emotion)) + 
            geom_bar(aes(y=..count.., fill=emotion)) + 
            scale_fill_brewer(palette="Dark2") + 
            ggtitle(title) + 
            theme(legend.position="right") + 
            ylab("Number of Tweets") + 
            xlab("Emotion Categories")
        }
    #plotting tweets emotions
    plotSentiments1(sent_df, "Analisis Sentimen Pencarian : Indomie (EN)")
  })
    
    output$NBPolarity <- renderPlot({
    plotSentiments2 <- function(sent_df, title)
        {
          library(ggplot2)
          ggplot(sent_df, aes(x=polarity)) +
            geom_bar(aes(y=..count.., fill=polarity)) +
            scale_fill_brewer(palette="RdGy") +
            ggtitle(title) +
            theme(legend.position="right") +
            ylab("Number of Tweets") +
            xlab("Polarity Categories")
        }
    #plotting tweets polarity
    plotSentiments2(sent_df, "Analisis Sentimen Pencarian : Indomie (EN)")
  })
}
shinyApp(ui = ui, server = server)
```


